---
title: "COVID-19 Case Fatality Rate: South Korea"
#author: "Byungwon Kim"
date: "3/27/2020"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("Code_functions_SCFR.r")
C <- read.csv("Korea_Agegroup_Cured.csv", header = TRUE, row.names = 1)
D <- read.csv("Korea_Agegroup_Dead.csv", header = TRUE, row.names = 1)
U <- read.csv("Korea_Agegroup_Unknown.csv", header = TRUE, row.names = 1)
N <- read.csv("Korea_Agegroup_Confirmed.csv", header = TRUE, row.names = 1)
colnames(C) <- c("0s","10s","20s","30s","40s","50s","60s","70s","80s")
colnames(D) <- c("0s","10s","20s","30s","40s","50s","60s","70s","80s")
colnames(U) <- c("0s","10s","20s","30s","40s","50s","60s","70s","80s")
colnames(N) <- c("0s","10s","20s","30s","40s","50s","60s","70s","80s")

FR.ours <- SCFR_estimation(D = D, U = U, C = C, N = N, model.option = 1)
FR.WHO1 <- SCFR_estimation(D = D, U = U, C = C, N = N, model.option = 2)
FR.WHO2 <- SCFR_estimation(D = D, U = U, C = C, N = N, model.option = 3)

FR.ours.collapsed <- SCFR_estimation(D = matrix(apply(D,1,sum), ncol = 1),
                                     U = matrix(apply(U,1,sum), ncol = 1),
                                     C = matrix(apply(C,1,sum), ncol = 1),
                                     N = matrix(apply(N,1,sum), ncol = 1), 
                                     model.option = 1)

```

## Trend of Daily Gross Case Fatality Rate

```{r figure_1_CFR, echo = FALSE, fig.height = 7, fig.width = 12}
y.limit <- c(-0.01, max(FR.ours$gross, 
                        FR.WHO1$gross, 
                        FR.WHO2$gross, 
                        FR.ours.collapsed$gross) + 0.01)
nt <- nrow(D)
days <- rownames(D)
par(mar = c(8,7,5,3))
plot(1:nt, FR.ours$gross, 
     type = "n", ylim = y.limit, xlim = c(0, nt + 1),
     ylab = "", xlab = "", xaxt = "n", yaxt = "n", cex.lab = 1.5)
polygon(c(1:nt, rev(1:nt)), c(FR.ours$gross.lower, rev(FR.ours$gross.upper)), 
        border = NA, col = "gray")
polygon(c(1:nt, rev(1:nt)), 
        c(FR.ours.collapsed$gross.lower, rev(FR.ours.collapsed$gross.upper)), 
        border = NA, col = "tan")
lines(1:nt, FR.WHO1$gross, type = "l", lty = 2, lwd = 2, col = "black",
      ylab = "", xlab = "")
lines(1:nt, FR.WHO2$gross, type = "l", lty = 3, lwd = 2, col = "black",
      ylab = "", xlab = "")
lines(1:nt, FR.ours$gross, type = "l", lty = 1, lwd = 2, col = "red",
      ylab = "", xlab = "")
lines(1:nt, FR.ours.collapsed$gross, type = "l", lty = 1, lwd = 2, col = "dodgerblue",
      ylab = "", xlab = "")
legend("topleft", 
       c("WHO 1st = # deaths / # confirmed", 
         "WHO 2nd = # deaths / (# deaths + # cured)", 
         "Our model - Age group stratification",
         "Our model - No group"), 
       col = c("black", "black", "red", "dodgerblue"), 
       lty = c(2,3,1,1),
       lwd = c(2,2,2,2),
       cex = 1.2)
axis(side = 1, at = c(1, seq(5, length(days)-1, by = 5), length(days)),
     labels = days[c(1, seq(5, length(days)-1, by = 5), length(days))],
     las = 2, cex.axis = 1.5)
axis(side = 2, at = seq(0, y.limit[2], by = 0.05),
     labels = paste0(seq(0, round(y.limit[2] * 100, 0), by = 5), "%"),
     las = 1, cex.axis = 1.5)

```

## Latest Age Group-wise Case Fatality Rates

```{r figure_2_agegroup_ci, echo = FALSE, fig.height = 7, fig.width = 12}
par(mar = c(3, 7, 5, 3))
plot(seq(0, max(FR.ours$group.upper)+0.05, length.out = 11),
     seq(0:10), type = "n", ylim = c(0,10.5), xlim = c(0, max(FR.ours$group.upper)+0.05),
     ylab = "", xlab = "",
     xaxt = "n", yaxt = "n")
points(FR.ours$gross[length(days)], 10, pch = 1, lwd = 10, col = "dodgerblue")
lines(c(FR.ours$gross.lower[length(days)],
        FR.ours$gross.upper[length(days)]),
      rep(10, 2),
      type = "b", lty = 1, pch = 4, lwd = 5, col = "seagreen")
for(i in 1:9){
  points(FR.ours$group[nrow(FR.ours$group),i], i, pch = 1, lwd = 10, col = "dodgerblue")
  lines(c(FR.ours$group.lower[nrow(FR.ours$group),i], 
          FR.ours$group.upper[nrow(FR.ours$group),i]),
        rep(i, 2), 
        type = "b", lty = 1, pch = 4, lwd = 5, col = "seagreen")
}
axis(side = 3, at = seq(0, 0.35, by = 0.05),
     labels = paste0(seq(0, 35, by = 5), "%"),
     las = 1, cex.axis = 1.5)
axis(side = 2, at = 1:10,
     labels = c("0 - 9", "10 - 19", "20 - 29", "30 - 39", "40 - 49",
                "50 - 59", "60 - 69", "70 - 79", "over 80", "Gross"),
     las = 2, cex.axis = 1.5)

```

```{r table_1_CFR, echo = FALSE}
library(DT)
Today <- length(FR.ours$gross)
CFR.Gross.table <- data.frame(CFR = c(round(as.numeric(FR.ours$gross[Today]) * 100, 2),
                                      round(as.numeric(FR.ours$group[Today,]) * 100, 2)),
                              SE = c(round(sqrt(as.numeric(FR.ours$gross.variance[Today])) * 100, 2),
                                     round(sqrt(as.numeric(FR.ours$group.variance[Today,])) * 100, 2)),
                              Lower = c(round(as.numeric(FR.ours$gross.lower[Today]) * 100, 2),
                                      round(as.numeric(FR.ours$group.lower[Today,]) * 100, 2)),
                              Upper = c(round(as.numeric(FR.ours$gross.upper[Today]) * 100, 2),
                                      round(as.numeric(FR.ours$group.upper[Today,]) * 100, 2)))
colnames(CFR.Gross.table) <- c("Fatality Rate (%)", 
                               "SE (%)", 
                               "95% confidence lower bound (%)", 
                               "95% confidence upper bound (%)")
rownames(CFR.Gross.table) <- c("Gross", colnames(FR.ours$group))
datatable(CFR.Gross.table, options = list(pageLength = 10))
```

## Age Group-wise data table

#### 1. Cumulative number of confirmed patients

```{r table_2_confirmed, echo = FALSE}
N.table <- data.frame(Date = rownames(N),
                      Total = apply(N, 1, sum),
                      N)
colnames(N.table) <- c("Date", "Total", colnames(N))
rownames(N.table) <- c()
datatable(N.table[nrow(N.table):1,], options = list(pageLength = 5))
```

#### 2. Cumulative number of deceased patients

```{r table_3_deceased, echo = FALSE}
D.table <- data.frame(Date = rownames(D),
                      Total = apply(D, 1, sum),
                      D)
colnames(D.table) <- c("Date", "Total", colnames(D))
rownames(D.table) <- c()
datatable(D.table[nrow(D.table):1,], options = list(pageLength = 5))
```

#### 3. Cumulative number of recovered patients

```{r table_4_recovered, echo = FALSE}
C.table <- data.frame(Date = rownames(C),
                      Total = apply(C, 1, sum),
                      C)
colnames(C.table) <- c("Date", "Total", colnames(C))
rownames(C.table) <- c()
datatable(C.table[nrow(C.table):1,], options = list(pageLength = 5))
```

##### *Data source*
  * ###### *Daily updated age grouped data can be downloaded from the below link:*
    ###### https://www.kaggle.com/kimjihoo/coronavirusdataset#TimeAge.csv
  * ###### *If not properly updated, the data can be manually recorded from the daily report published by KCDC*
    ###### http://ncov.mohw.go.kr/tcmBoardList.do?brdId=3&brdGubun=&dataGubun=&ncvContSeq=&contSeq=&board_id=

